Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2017-12-04 PAPER.tex
made sure none of the plots are cut off

\begin{figure}
	\centering
	\includegraphics[trim={1.5cm 0.2cm 3.5cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss1.png}
	\caption{Our toy model dataset. We model a mock foreground-only visibility with a sinusoid signal that varies smoothly in 
time and frequency. We model a mock EoR signal as a random Gaussian signal. Real parts are shown here.}
	\label{fig:toy_sigloss1}
\end{figure}

@@

\begin{figure*}
	\centering
	\includegraphics[trim={0.3cm 0.2cm 1cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss3.png}
	\includegraphics[trim={1cm 0.2cm 0cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss4.png}
	\caption{Resulting power spectrum estimates for the toy model simulation described in Section \ref{sec:toymodel} --- 
foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green). The power spectrum of foregrounds peaks at a $k$ mode based on the frequency of the sinusoid used to create the mock FG signal. In the two panels, we compare inverse covariance weighting 
where $\textbf{C}$ is derived from the data (left),and projecting out the first eigenmode only (right). In the former 
case, signal loss arises from using information from all eigenmodes of $\hat{\textbf{C}}$. Because $\hat{\textbf{C}}$ is 
empirically estimated, its eigenvalues pose the risk of describing EoR-dominating modes. Consequently, these modes are over-fitted and down-weighted, leading to signal loss. 
There is no signal loss when using only the zeroth eigenmode, since we are not using information from the weaker eigenmodes 
which $\hat{\textbf{C}}$ does not describe accurately.}
	\label{fig:toy_sigloss3}
\end{figure*}

@@

\begin{figure}
	\centering
	\includegraphics[trim={0.3cm 0.2cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss2.png}
	\caption{Eigenspectrum of $\hat{\textbf{C}}_{FG}$ (blue), $\hat{\textbf{C}}_{EoR}$ (red), and $\hat{\textbf{C}}_{FG+EoR}$ 
(green). The eigenspectrum of $\hat{\textbf{C}}_{FG}$ peaks at the zeroth eigenmode, due to the presence of only one 
sinusoid. These empirically estimated covariance matrices have eigenspectra that are different from that of a true $\textbf{C}$, 
meaning that some eigenmodes (shapes in the data) may be down-weighted more significantly than they should be, producing 
signal loss. Specifically, down-weighting the weak eigenmodes, where the EoR signal is greater than the FG signal, leads to 
loss.}
	\label{fig:toy_sigloss2}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[trim={1.5cm 0.1cm 3.5cm 0.1cm},clip,width=\columnwidth]{plots/toy_sigloss12.png}
	\includegraphics[trim={1.5cm 0.1cm 3.5cm 0.1cm},clip,width=\columnwidth]{plots/toy_sigloss13.png}
	\caption{The covariance matrices (top row) and inverse covariance-weighted data (bottom row) for FG only (left), EoR only 
(middle), and FG + EoR (right). Real parts are shown here.}
	\label{fig:toy_sigloss12}
\end{figure}

@@

The resulting eigenspectrum as compared to the green curve (FG + EoR) in Figure \ref{fig:toy_sigloss2} is shown in Figure 
\ref{fig:toy_sigloss5} (right plot). The spectrum, in the case of fringe-rate filtering (dashed line), falls more steeply, especially for 
the last few eigenmodes. In many applications, this steep fall is not indicative of the true covariance structure of the data. With 
fringe-rate filtering resulting in fewer independent modes, it becomes more difficult for the empirical covariance to estimate the 
true covariance matrix. This can be quantified by evaluating a convergence metric $\varepsilon$ for the empirical covariance, which we define as
\begin{equation}
\label{eq:converge}
\varepsilon (\Chat) \equiv \sqrt{\frac{\sum_{ij} (\Chat_{ij} - \C_{ij})^2}{\sum_{ij} \C_{ij}^2}},
\end{equation}
where $\C$ is true covariance matrix. In Figure \ref{toy_sigloss16} we show this convergence statistic as a function of the number of independent ensemble realizations in one's simulations (horizontal axis) and the number of independent samples in the data following fringe-rate filtering (different curve colors). With more independent time samples in the data, one converges to the true covariance more quickly. The situation here with using a finite number of time samples to estimate our covariance is analogous to a problem faced in galaxy surveys, where the non-linear covariance 
of the matter power spectrum is estimated using a large --- but finite --- number of expensive simulations. There, the limited 
number of independent simulations results in inaccuracies in estimated covariance matrices 
\citep{dodelson_schneider2013,taylor_joachimi_etal2014}, which in turn result in biases in the final parameter constraints 
\citep{hartlap_et_al2007}. In our case, the empirically estimated covariances are used for estimating the power spectrum, and 
as we argue in Section \ref{sec:siglossmethod} and Appendix \ref{sec:sigloss_appendix}, the resulting estimates are biased 
\emph{low}---which is precisely signal loss. In future work, it will be fruitful to investigate whether advanced techniques from the 
galaxy survey literature for estimating accurate covariance matrices can be successfully adapted for $21\,\textrm{cm}$ 
cosmology. These techniques include the imposition of sparsity priors \citep{padmanabhan_et_al2016}, the fitting of 
theoretically motivated parametric forms \citep{pearson_samushia2016}, covariance tapering \citep{paz_sanchez2015}, 
marginalization over the true covariance \citep{sellentin_heavens2016}, and shrinkage methods 
\citep{pope_szapudi2008,joachimi_2017}.

\begin{figure*}
	\centering
	\includegraphics[trim={1.5cm 0.2cm 1.5cm 0.3cm},clip,height=0.29\textwidth]{plots/toy_sigloss5.png}
	\includegraphics[trim={0.3cm 0.2cm 0.3cm 0.3cm},clip,height=0.29\textwidth]{plots/toy_sigloss15.png}
	\caption{Left: Our `fringe-rate filtered' (time-averaged) toy model dataset. We average every four samples together, 
yielding $25$ independent samples in time. Real parts are shown here. Right: Eigenspectrum of $\hat{\textbf{C}}_{FG+EoR}$, 
in the case of no fringe-rate filtering (solid green) and with fringe-rate filtering (dashed green). The dashed spectrum is steeper, 
resulting in more dramatic differences in weighting between eigenmodes. Consequently, if all eigenmodes are used in weighting 
it is possible to down-weight EoR modes more severely than for the non-averaged case.}
	\label{fig:toy_sigloss5}
\end{figure*}

\begin{figure}
	\centering
	\includegraphics[trim={0.3cm 0.2cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss7.png}
	\caption{Resulting power spectrum estimate for the `fringe-rate filtered' (time-averaged) toy model simulation --- foregrounds only (blue), 
EoR only (red), and the weighted FG + EoR dataset (green). We use inverse covariance weighting where $\textbf{C}$ is 
computed from the data. There is a larger amount of signal loss than for the non-averaged data, a consequence of a 
steepened, weakly characterized eigenspectrum from fewer independent modes in the data. The power spectrum 
estimate is also noisier, since most of the information used in constructing the estimate came from only a few eigenmodes (the 
weakest, EoR-dominated modes).}
	\label{fig:toy_sigloss7}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[trim={0.3cm 0cm 0.3cm 0.2cm},clip,width=\columnwidth]{plots/toy_sigloss16.png}
	\caption{The convergence level, as defined in Equation \eqref{eq:converge}, of empirically estimated covariances of mock EoR signals with different numbers of independent samples. In red, the mock EoR signal is comprised entirely of independent samples. Subsequent colors show time-averaged signals. As the number of realizations increases, we see that the empirical covariances approach the true covariances. With more independent samples, the quicker an empirical covariance converges.}
	\label{fig:toy_sigloss16}
\end{figure}

The power spectrum results for the fringe-rate filtered toy model data is shown in Figure \ref{fig:toy_sigloss7}. As 
expected, there is a much larger amount of signal loss for this time-averaged dataset. Additionally, because of the steepened 
eigenspectrum, the last few eigenmodes receive more weight relative to the others. Therefore, most of our power spectrum 
information is coming from only these last few modes and as a result, it is a noisier estimate. This is evident by noticing that the 
green curve in Figure \ref{fig:toy_sigloss7} fails to trace the shape of the unweighted EoR power spectrum.

@@

\begin{figure}
	\centering
	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss14.png}
	\caption{We compare the eigenspectrum of an empirically calculated $\hat{\textbf{C}}$ (green) to that of four alternate 
weighting options, including modeling the covariance matrix of EoR (red), regularizing $\hat{\textbf{C}}$ by adding an identity 
matrix to it (blue), using only the first three eigenmodes of $\hat{\textbf{C}}$ (yellow), and multiplying an identity matrix with $
\hat{\textbf{C}}$ (magenta). All eigenspectra (except the green) are relatively flat and don't exhibit signal loss. All were 
computed for the `fringe-rate filtered' (time-averaged) toy model case.}
	\label{fig:toy_sigloss14}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_error1.png}
	\caption{Error estimation from bootstrapping as a function of the number of elements drawn per bootstrap when 
sampling with replacement. The star represents the standard deviation of $N_{boot}$ bootstraps, each created by drawing $1000$ 
elements (with replacement) from a length $1000$ array of a Gaussian random signal. The black points correspond to time-averaged data (correlated data) which has $100$ independent samples. They illustrate how errors can be under-estimated if 
drawing more elements than there are independent samples in the data. The estimated errors match up with the theoretical 
prediction only at $N=100$.}
	\label{fig:toy_error1}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_error2.png}
	\caption{The fraction of independent elements in one bootstrap sample as a function of the total number of elements in a 
dataset (i.e. if $4$ out of $5$ elements are independent, this would yield a fraction of $0.8$). A fraction of $1.0$ means that all 
elements in the bootstrap sample are independent, and therefore sensitivity is maximized (alternately, this axis can be thought 
of as power spectrum sensitivity, where sensitivity increases moving upwards along the y-axis). Two bootstrapping methods are shown here --- sampling all elements with replacement (gray) and sampling only the last element with replacement (black). The former fails to maximize sensitivity since some elements end up being repeated due to random sampling.} 
%The `outlier' points lying at a fraction of $1.0$ at the far left of the plot occur in the off-chance that the last spot in the sample happens to be the one missing element instead of a repeated element --- this is more likely to happen with a small total number of elements but also results in a more dramatically different fraction as compared to the case of a repeated element in the last spot, hence why these points appear like outliers.}
	\label{fig:toy_error2}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_bias1.png}
	\caption{Power spectrum estimates for a null jackknife test with the presence of a foreground systematic (blue), without 
the foreground systematic (red), and noise alone (green). Because the first null test is not consistent with noise, it suggests the 
presence of a systematic in either $\textbf{x}_{1}$ or $\textbf{x}_{2}$. Null tests of clean measurements should be consistent 
with thermal noise.}
	\label{fig:toy_bias1}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_bias2.png}
	\caption{Power spectrum estimates for $\textbf{x}_{1}$ and $\textbf{x}_{2}$, two jackknives of the toy model. They suggest 
the presence of a systematic in $\textbf{x}_{1}$ only, illustrating how jackknives can be used to tease out excesses. Clean 
measurements should remain consistent despite the jackknife taken.}
	\label{fig:toy_bias2}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},width=\columnwidth]{plots/data_errors.png}
	\caption{$2\sigma$ power spectrum errors (not upper limits) using PAPER-64 data and three different bootstrapping 
methods. The data is fringe-rate filtered and a weighting matrix of $\textbf{I}$ (unweighted) is used in order to disentangle the 
effects of bootstrapping from signal loss. Three different bootstrapping methods are shown: the blue and black use methods 
where bootstrapping occurs on the baseline axis only (not the time axis), and they differ by how the baselines are randomly 
sampled. It is evident that sensitivity is maximized when baselines are sampled in a way that ensures mostly independent 
samples (only the last baseline spot is sampled randomly), as shown by the black curve. In red, bootstrapping occurs over both 
the baseline and time axes, illustrating how errors can be under-estimated if sampling more values than independent ones 
(fringe-rate filtering reduces the number of independent samples). We use the method illustrated by the black curve in our 
updated analysis, which is shown to agree with the $2\sigma$ analytic prediction for noise (green).}
	\label{fig:data_errors}
\end{figure}

>>>>

\begin{figure}
	\centering
	\includegraphics[trim={1.5cm 0cm 3.5cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss1.png}
	\caption{Our toy model dataset. We model a mock foreground-only visibility with a sinusoid signal that varies smoothly in 
time and frequency. We model a mock EoR signal as a random Gaussian signal. Real parts are shown here.}
	\label{fig:toy_sigloss1}
\end{figure}

@@

\begin{figure*}
	\centering
	\includegraphics[trim={0.3cm 0cm 1cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss3.png}
	\includegraphics[trim={1cm 0cm 0cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss4.png}
	\caption{Resulting power spectrum estimates for the toy model simulation described in Section \ref{sec:toymodel} --- 
foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green). The power spectrum of foregrounds peaks at a $k$ mode based on the frequency of the sinusoid used to create the mock FG signal. In the two panels, we compare inverse covariance weighting 
where $\textbf{C}$ is derived from the data (left),and projecting out the first eigenmode only (right). In the former 
case, signal loss arises from using information from all eigenmodes of $\hat{\textbf{C}}$. Because $\hat{\textbf{C}}$ is 
empirically estimated, its eigenvalues pose the risk of describing EoR-dominating modes. Consequently, these modes are over-fitted and down-weighted, leading to signal loss. 
There is no signal loss when using only the zeroth eigenmode, since we are not using information from the weaker eigenmodes 
which $\hat{\textbf{C}}$ does not describe accurately.}
	\label{fig:toy_sigloss3}
\end{figure*}

@@

\begin{figure}
	\centering
	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss2.png}
	\caption{Eigenspectrum of $\hat{\textbf{C}}_{FG}$ (blue), $\hat{\textbf{C}}_{EoR}$ (red), and $\hat{\textbf{C}}_{FG+EoR}$ 
(green). The eigenspectrum of $\hat{\textbf{C}}_{FG}$ peaks at the zeroth eigenmode, due to the presence of only one 
sinusoid. These empirically estimated covariance matrices have eigenspectra that are different from that of a true $\textbf{C}$, 
meaning that some eigenmodes (shapes in the data) may be down-weighted more significantly than they should be, producing 
signal loss. Specifically, down-weighting the weak eigenmodes, where the EoR signal is greater than the FG signal, leads to 
loss.}
	\label{fig:toy_sigloss2}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[trim={1.5cm 0cm 3.5cm 0.1cm},clip,width=\columnwidth]{plots/toy_sigloss12.png}
	\includegraphics[trim={1.5cm 0cm 3.5cm 0.1cm},clip,width=\columnwidth]{plots/toy_sigloss13.png}
	\caption{The covariance matrices (top row) and inverse covariance-weighted data (bottom row) for FG only (left), EoR only 
(middle), and FG + EoR (right). Real parts are shown here.}
	\label{fig:toy_sigloss12}
\end{figure}

@@

The resulting eigenspectrum as compared to the green curve (FG + EoR) in Figure \ref{fig:toy_sigloss2} is shown in Figure 
\ref{fig:toy_sigloss5} (right plot). The spectrum, in the case of fringe-rate filtering (dashed line), falls more steeply, especially for 
the last few eigenmodes. In many applications, this steep fall is not indicative of the true covariance structure of the data. With 
fringe-rate filtering resulting in fewer independent modes, it becomes more difficult for the empirical covariance to estimate the 
true covariance matrix. This can be quantified by evaluating a convergence metric $\varepsilon$ for the empirical covariance, which we define as
\begin{equation}
\label{eq:converge}
\varepsilon (\Chat) \equiv \sqrt{\frac{\sum_{ij} (\Chat_{ij} - \C_{ij})^2}{\sum_{ij} \C_{ij}^2}},
\end{equation}
where $\C$ is true covariance matrix. In Figure \ref{fig:toy_sigloss16} we show this convergence statistic as a function of the number of independent ensemble realizations in one's simulations (horizontal axis) and the number of independent samples in the data following fringe-rate filtering (different curve colors). With more independent time samples in the data, one converges to the true covariance more quickly.

The situation here with using a finite number of time samples to estimate our covariance is analogous to a problem faced in galaxy surveys, where the non-linear covariance 
of the matter power spectrum is estimated using a large --- but finite --- number of expensive simulations. There, the limited 
number of independent simulations results in inaccuracies in estimated covariance matrices 
\citep{dodelson_schneider2013,taylor_joachimi_etal2014}, which in turn result in biases in the final parameter constraints 
\citep{hartlap_et_al2007}. In our case, the empirically estimated covariances are used for estimating the power spectrum, and 
as we argue in Section \ref{sec:siglossmethod} and Appendix \ref{sec:sigloss_appendix}, the resulting estimates are biased 
\emph{low}---which is precisely signal loss. In future work, it will be fruitful to investigate whether advanced techniques from the 
galaxy survey literature for estimating accurate covariance matrices can be successfully adapted for $21\,\textrm{cm}$ 
cosmology. These techniques include the imposition of sparsity priors \citep{padmanabhan_et_al2016}, the fitting of 
theoretically motivated parametric forms \citep{pearson_samushia2016}, covariance tapering \citep{paz_sanchez2015}, 
marginalization over the true covariance \citep{sellentin_heavens2016}, and shrinkage methods 
\citep{pope_szapudi2008,joachimi_2017}.

\begin{figure*}
	\centering
	\includegraphics[trim={1.5cm 0cm 1.5cm 0.3cm},clip,height=0.29\textwidth]{plots/toy_sigloss5.png}
	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},clip,height=0.29\textwidth]{plots/toy_sigloss15.png}
	\caption{Left: Our `fringe-rate filtered' (time-averaged) toy model dataset. We average every four samples together, 
yielding $25$ independent samples in time. Real parts are shown here. Right: Eigenspectrum of $\hat{\textbf{C}}_{FG+EoR}$, 
in the case of no fringe-rate filtering (solid green) and with fringe-rate filtering (dashed green).}
	\label{fig:toy_sigloss5}
\end{figure*}

\begin{figure}
	\centering
	\includegraphics[trim={0cm 0cm 0.3cm 0.2cm},clip,width=\columnwidth]{plots/toy_sigloss7.png}
	\caption{Resulting power spectrum estimate for the `fringe-rate filtered' (time-averaged) toy model simulation --- foregrounds only (blue), 
EoR only (red), and the weighted FG + EoR dataset (green). We use inverse covariance weighting where $\textbf{C}$ is 
computed from the data. There is a larger amount of signal loss than for the non-averaged data, a consequence of a 
steepened, weakly characterized eigenspectrum from fewer independent modes in the data. The power spectrum 
estimate is also noisier, since most of the information used in constructing the estimate came from only a few eigenmodes (the 
weakest, EoR-dominated modes).}
	\label{fig:toy_sigloss7}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[trim={0cm 0cm 0.3cm 0.2cm},clip,width=\columnwidth]{plots/toy_sigloss16.png}
	\caption{The convergence level, as defined in Equation \eqref{eq:converge}, of empirically estimated covariances of mock EoR signals with different numbers of independent samples. In red, the mock EoR signal is comprised entirely of independent samples. Subsequent colors show time-averaged signals. As the number of realizations increases, we see that the empirical covariances approach the true covariances. With more independent samples, the quicker an empirical covariance converges.}
	\label{fig:toy_sigloss16}
\end{figure}

The power spectrum results for the fringe-rate filtered toy model data is shown in Figure \ref{fig:toy_sigloss7}. As 
expected, there is a much larger amount of signal loss for this time-averaged dataset. We do a worse job estimating the true covariance and, as a result, it is a noisier estimate. This is evident by noticing that the 
green curve in Figure \ref{fig:toy_sigloss7} fails to trace the shape of the unweighted EoR power spectrum.

@@

\begin{figure}
	\centering
	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss14.png}
	\caption{We compare the eigenspectrum of an empirically calculated $\hat{\textbf{C}}$ (green) to that of four alternate 
weighting options, including modeling the covariance matrix of EoR (red), regularizing $\hat{\textbf{C}}$ by adding an identity 
matrix to it (blue), using only the first three eigenmodes of $\hat{\textbf{C}}$ (yellow), and multiplying an identity matrix with $
\hat{\textbf{C}}$ (magenta). All eigenspectra (except the green) are relatively flat and don't exhibit signal loss. All were 
computed for the `fringe-rate filtered' (time-averaged) toy model case.}
	\label{fig:toy_sigloss14}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_error1.png}
	\caption{Error estimation from bootstrapping as a function of the number of elements drawn per bootstrap when 
sampling with replacement. The star represents the standard deviation of $N_{boot}$ bootstraps, each created by drawing $1000$ 
elements (with replacement) from a length $1000$ array of a Gaussian random signal. The black points correspond to time-averaged data (correlated data) which has $100$ independent samples. They illustrate how errors can be under-estimated if 
drawing more elements than there are independent samples in the data. The estimated errors match up with the theoretical 
prediction only at $N=100$.}
	\label{fig:toy_error1}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_error2.png}
	\caption{The fraction of independent elements in one bootstrap sample as a function of the total number of elements in a 
dataset (i.e. if $4$ out of $5$ elements are independent, this would yield a fraction of $0.8$). A fraction of $1.0$ means that all 
elements in the bootstrap sample are independent, and therefore sensitivity is maximized (alternately, this axis can be thought 
of as power spectrum sensitivity, where sensitivity increases moving upwards along the y-axis). Two bootstrapping methods are shown here --- sampling all elements with replacement (gray) and sampling only the last element with replacement (black). The former fails to maximize sensitivity since some elements end up being repeated due to random sampling.} 
%The `outlier' points lying at a fraction of $1.0$ at the far left of the plot occur in the off-chance that the last spot in the sample happens to be the one missing element instead of a repeated element --- this is more likely to happen with a small total number of elements but also results in a more dramatically different fraction as compared to the case of a repeated element in the last spot, hence why these points appear like outliers.}
	\label{fig:toy_error2}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_bias1.png}
	\caption{Power spectrum estimates for a null jackknife test with the presence of a foreground systematic (blue), without 
the foreground systematic (red), and noise alone (green). Because the first null test is not consistent with noise, it suggests the 
presence of a systematic in either $\textbf{x}_{1}$ or $\textbf{x}_{2}$. Null tests of clean measurements should be consistent 
with thermal noise.}
	\label{fig:toy_bias1}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_bias2.png}
	\caption{Power spectrum estimates for $\textbf{x}_{1}$ and $\textbf{x}_{2}$, two jackknives of the toy model. They suggest 
the presence of a systematic in $\textbf{x}_{1}$ only, illustrating how jackknives can be used to tease out excesses. Clean 
measurements should remain consistent despite the jackknife taken.}
	\label{fig:toy_bias2}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},width=\columnwidth]{plots/data_errors.png}
	\caption{$2\sigma$ power spectrum errors (not upper limits) using PAPER-64 data and three different bootstrapping 
methods. The data is fringe-rate filtered and a weighting matrix of $\textbf{I}$ (unweighted) is used in order to disentangle the 
effects of bootstrapping from signal loss. Three different bootstrapping methods are shown: the blue and black use methods 
where bootstrapping occurs on the baseline axis only (not the time axis), and they differ by how the baselines are randomly 
sampled. It is evident that sensitivity is maximized when baselines are sampled in a way that ensures mostly independent 
samples (only the last baseline spot is sampled randomly), as shown by the black curve. In red, bootstrapping occurs over both 
the baseline and time axes, illustrating how errors can be under-estimated if sampling more values than independent ones 
(fringe-rate filtering reduces the number of independent samples). We use the method illustrated by the black curve in our 
updated analysis, which is shown to agree with the $2\sigma$ analytic prediction for noise (green).}
	\label{fig:data_errors}
\end{figure}
